---
title: "BUAN6356- Project" - GROUP 3 - Telco Customer Churn
                          Focused customer retention programs
output: html_document
---
Installing the required packages

```{r}
# install.packages("tree")
# install.packages("caTools")
# install.packages("randomForest")
# install.packages("e1071")
# install.packages("lubridate")
# install.packages("MASS")
# install.packages("caret")
# install.packages("e1071")
# install.packages("lubridate")
install.packages("pls")
# install.packages("dplyr")
 install.packages("gridExtra")
```

# libraries 
```{r}
library(tidyverse)
library(modelr)
library(lubridate) # for date and time
library(caTools)   # for splitting the dataset
library(class)
library(MASS)
library(tree)
library(ISLR)
require(tree)
library(randomForest)
library(caret)   # for support vector machine
library(dplyr)
library(gridExtra)
library(ROCR)

# getting the current directory
getwd() 

# importing the dataset
teleco <-  read.csv("Telco-Customer.csv") 
names(teleco)
head(teleco)

```

# Finding the unique values for each of the predictors

```{r}
unique(teleco$gender) 
# Levels: Female Male
unique(teleco$SeniorCitizen)
# Levels: 0 1
unique(teleco$Partner)
# Levels: No Yes
unique(teleco$Dependents)
# Levels: Female Male
unique(teleco$PhoneService)
# Levels: No Yes
unique(teleco$MultipleLines)
# Levels: No, No phone service, Yes
unique(teleco$InternetService)
# Levels: DSL Fiber optic No
unique(teleco$OnlineSecurity)
#Levels: No ,No internet service, Yes
unique(teleco$OnlineBackup)
#Levels: No No internet service Yes
unique(teleco$DeviceProtection)
# Levels: No, No internet service ,Yes
unique(teleco$TechSupport)
# Levels: No, No internet service, Yes
unique(teleco$StreamingTV)
# Levels: No, No internet service ,Yes
unique(teleco$StreamingMovies)
# Levels: No, No internet service ,Yes
unique(teleco$Contract)
# Levels: Month-to-month, One year, Two year
unique(teleco$PaperlessBilling)
# Levels: No Yes
unique(teleco$PaymentMethod)
# Levels: Bank transfer (automatic), Credit card (automatic) ,Electronic check, Mailed check

```

# Checking whether the variable is having null values and getting the count

```{r}
sum(is.na(teleco$gender)) # 0
sum(is.na(teleco$SeniorCitizen)) # 0
sum(is.na(teleco$Partner)) # 0
sum(is.na(teleco$Dependents)) # 0
sum(is.na(teleco$PhoneService)) # 0
sum(is.na(teleco$MultipleLines)) # 0
sum(is.na(teleco$InternetService)) # 0
sum(is.na(teleco$OnlineSecurity)) # 0
sum(is.na(teleco$OnlineBackup))  # 0
sum(is.na(teleco$DeviceProtection)) # 0
sum(is.na(teleco$TechSupport)) # 0
sum(is.na(teleco$StreamingTV)) # 0
sum(is.na(teleco$StreamingMovies)) # 0
sum(is.na(teleco$Contract)) # 0
sum(is.na(teleco$PaperlessBilling)) # 0
sum(is.na(teleco$PaymentMethod)) # 0
sum(is.na(teleco$TotalCharges)) # 11

```


# As the total charges is having 11 N/A values we are replacing it with the mean value of the totalcharges.

```{r}
# checking the row number with NA values in TotalCharges column
which(is.na(teleco$TotalCharges))
# 489  754  937 1083 1341 3332 3827 4381 5219 6671 6755

# omitting the rows with NA values in Totalcharges column
telco_na_rm <- na.omit(teleco, cols = "TotalCharges")

# Finding  the mean of the column                                
telco_tchg_mean <- mean(telco_na_rm$TotalCharges)

# replacing the NA values in Total charges column with the mean value
teleco$TotalCharges[c(489,754,937,1083,1341,3332,3827,4381,5219,6671,6755)] <-  telco_tchg_mean

```


```{r}
# Plots
# Plotting the first 4 predictors against churn and checking if it conveys any 
# relationship with churn

plot1 <- ggplot(data = teleco, aes(x = teleco$gender, fill = teleco$Churn)) +
         geom_bar(position = "fill") +
         theme_bw() +
  labs( x= "Gender", y =" Churn")

plot2 <- ggplot(data = teleco, aes(x = teleco$SeniorCitizen, fill = teleco$Churn)) +
         geom_bar(position = "fill") +
         theme_bw()+
  labs( x= "Senior Citizen", y =" Churn")

plot3 <- ggplot(data = teleco, aes(x =teleco$Partner, fill = teleco$Churn)) +
         geom_bar(position = "fill") +
         theme_bw()+
  labs( x= "Partner", y =" Churn")

plot4 <- ggplot(data = teleco, aes(x = teleco$Dependents, fill = teleco$Churn)) +
         geom_bar(position = "fill")+
         theme_bw()+
  labs( x= "Dependents", y =" Churn")

grid.arrange(plot1, plot2, plot3, plot4, ncol=2)

# Next 4 predictors.
plot5 <- ggplot(data = teleco, aes(x = teleco$PhoneService, fill = teleco$Churn)) +
         geom_bar(position = "fill") +
         theme_bw()+
  labs( x= "Phone Service", y =" Churn")

plot6 <- ggplot(data = teleco, aes(x = teleco$MultipleLines, fill = teleco$Churn)) +
         geom_bar(position = "fill") +
         theme_bw()+
  labs( x= "Multiple Lines", y =" Churn")

plot7 <- ggplot(data = teleco, aes(x = teleco$InternetService, fill = teleco$Churn)) +
         geom_bar(position = "fill")+
         theme_bw()+
  labs( x= "Internet Services", y =" Churn")

plot8 <- ggplot(data = teleco, aes(x = teleco$OnlineSecurity, fill = teleco$Churn)) +
         geom_bar(position = "fill")+
         theme_bw()+
  labs( x= "Online Security", y =" Churn")

grid.arrange(plot5, plot6, plot7, plot8, ncol=2)
# Next 4 predictors.

plot9 <- ggplot(data = teleco, aes(x = teleco$OnlineBackup, fill = teleco$Churn)) +
         geom_bar(position = "fill")+
         theme_bw()+
  labs( x= "Online Backup", y =" Churn")

plot10 <- ggplot(data = teleco, aes(x = teleco$DeviceProtection, fill = teleco$Churn))+
          geom_bar(position = "fill")+
         theme_bw()+
  labs( x= "Device Protection", y =" Churn")

plot11 <- ggplot(data = teleco, aes(x = teleco$TechSupport, fill = teleco$Churn)) +
          geom_bar(position = "fill") +
         theme_bw()+
  labs( x= "Tech Support", y =" Churn")

plot12 <- ggplot(data = teleco, aes(x = teleco$StreamingTV, fill = teleco$Churn)) +
          geom_bar(position = "fill") +
         theme_bw()+
  labs( x= "Streaming TV", y =" Churn")

grid.arrange(plot9, plot10, plot11, plot12, ncol=2)

# Next 4 predictors.
plot13 <- ggplot(data = teleco, aes(x = teleco$StreamingMovies, fill = teleco$Churn))+
          geom_bar(position = "fill") +
         theme_bw()+
  labs( x= "Streaming Movies", y =" Churn")

plot14 <- ggplot(data = teleco, aes(x = teleco$Contract, fill = teleco$Churn)) +
          geom_bar(position = "fill")+
         theme_bw()+
  labs( x= "Contract", y =" Churn")

plot15 <- ggplot(data = teleco, aes(x = teleco$PaperlessBilling, fill = teleco$Churn))+
          geom_bar(position = "fill")+
         theme_bw()+
  labs( x= "Paperless Billing", y =" Churn")

plot16 <- ggplot(data = teleco, aes(x = teleco$PaymentMethod, fill = teleco$Churn)) +
          geom_bar(position = "fill")+
         theme_bw()+
  labs( x= "Payment Method", y =" Churn")

grid.arrange(plot13, plot14, plot15, plot16, ncol=2)

plot17 <- ggplot(data = teleco, aes(x = teleco$MonthlyCharges, fill = teleco$Churn)) +
   geom_bar()+
         theme_bw() +
  labs( x= "Monthly Charges", y =" Churn")

plot18<- ggplot(data = teleco, aes(x = teleco$TotalCharges, fill = teleco$Churn)) +
  geom_histogram(position = "fill", binwidth= 10)+
         theme_bw()+
  labs( x= "Total Charges", y =" Churn")

# The graphs and plots do not convey much information or relation with churn.
# Hence, the exploratory data analysis is not sufficient to predict that
# the customer will churn because of what reasons (predictors). 
#THe patterns displayed by the plots are insufficient to make analysis to 
#determine churn. Hence we proceed to next method of analysis. 

```
# Converting into dummy variables

```{r}
for(level in unique(teleco$gender)){
  teleco[paste("Gender", level, sep = "_")] <- ifelse(teleco$gender == level, 1, 0)
}

for(level in unique(teleco$SeniorCitizen)){
  teleco[paste("SeniorCitizen", level, sep = "_")] <- ifelse(teleco$SeniorCitizen == level, 1, 0)
}

for(level in unique(teleco$Partner)){
  teleco[paste("Partner", level, sep = "_")] <- ifelse(teleco$Partner == level, 1, 0)
}


for(level in unique(teleco$Dependents)){
  teleco[paste("Dependents", level, sep = "_")] <- ifelse(teleco$Dependents == level, 1, 0)
}

for(level in unique(teleco$PhoneService)){
  teleco[paste("PhoneService", level, sep = "_")] <- ifelse(teleco$PhoneService == level, 1, 0)
}


for(level in unique(teleco$MultipleLines)){
  teleco[paste("MultipleLines", level, sep = "_")] <- ifelse(teleco$MultipleLines == level, 1, 0)
}


for(level in unique(teleco$InternetService)){
  teleco[paste("InternetService", level, sep = "_")] <- ifelse(teleco$InternetService == level, 1, 0)
}


for(level in unique(teleco$OnlineSecurity)){
  teleco[paste("OnlineSecurity", level, sep = "_")] <- ifelse(teleco$OnlineSecurity == level, 1, 0)
}


for(level in unique(teleco$OnlineBackup)){
  teleco[paste("Online_Backup", level, sep = "_")] <- ifelse(teleco$OnlineBackup == level, 1, 0)
}


for(level in unique(teleco$DeviceProtection)){
  teleco[paste("DeviceProtection", level, sep = "_")] <- ifelse(teleco$DeviceProtection == level, 1, 0)
}

for(level in unique(teleco$TechSupport)){
  teleco[paste("TechSupport", level, sep = "_")] <- ifelse(teleco$TechSupport == level, 1, 0)
}

for(level in unique(teleco$StreamingTV)){
  teleco[paste("tv", level, sep = "_")] <- ifelse(teleco$StreamingTV == level, 1, 0)
}

for(level in unique(teleco$StreamingMovies)){
  teleco[paste("Movies", level, sep = "_")] <- ifelse(teleco$StreamingMovies == level, 1, 0)
}


for(level in unique(teleco$Contract)){
  teleco[paste("Contract", level, sep = "_")] <- ifelse(teleco$Contract == level, 1, 0)
}

for(level in unique(teleco$PaperlessBilling)){
  teleco[paste("PaperLessBilling", level, sep = "_")] <- ifelse(teleco$PaperlessBilling == level, 1, 0)
}

for(level in unique(teleco$PaymentMethod)){
  teleco[paste("PaymentMethod", level, sep = "_")] <- ifelse(teleco$PaymentMethod == level, 1, 0)
}

```
 
 # Deleting original categorical variables

```{r}
teleco_new <- teleco
teleco_new['gender'] <- NULL
teleco_new['SeniorCitizen'] <- NULL
teleco_new['Partner'] <- NULL
teleco_new['Dependents'] <- NULL
teleco_new['PhoneService'] <- NULL
teleco_new['MultipleLines'] <- NULL
teleco_new['InternetService'] <- NULL
teleco_new['OnlineSecurity'] <- NULL
teleco_new['OnlineBackup'] <- NULL
teleco_new['DeviceProtection'] <- NULL
teleco_new['TechSupport'] <- NULL
teleco_new['StreamingTV'] <- NULL
teleco_new['StreamingMovies'] <- NULL
teleco_new['Contract'] <- NULL
teleco_new['PaperlessBilling'] <- NULL
teleco_new['PaymentMethod'] <- NULL

```

## Splitting the data into training and testing data

```{r}
split_factor <- sample.split(teleco_new,SplitRatio = 0.8) # to split the dataset into test and training dataset by
                                                          # a ratio of 0.8 that is 80% training and 20% testing

teleco_train <- subset(teleco_new, split_factor == 'TRUE') # assigning the data which is having the split_factor = TRUE 
                                                           # from the Data1 dataset to a training dataset
teleco_test  <- subset(teleco_new,split_factor == 'FALSE') # assigning the data which is having the split_factor = FALSE  
                                                           # from the Data1 dataset to a training dataset
```
teleco_train
Removing the customerID column from both training and testing data set

```{r}
colnames(teleco)

teleco_train_1 <- teleco_train
teleco_train_1['customerID'] <- NULL

teleco_test_1 <- teleco_test
teleco_test_1['customerID'] <- NULL
```

# Model -1 - Logistic Regression model with threshold value 0.5

```{r}

model1<-glm(Churn~ .,family=binomial,data = teleco_train_1)
summary(model1)
teleco_test_1$probability<-predict(model1,teleco_test_1,type='response')
teleco_test_1$pred<-'No'
teleco_test_1$pred[teleco_test_1$probability>0.5]<-'Yes'

# Confusion matrix
Confusion_model1 <- with(teleco_test_1,table(pred,Churn))
with(teleco_test_1, mean(pred==Churn))

# write.csv(MyData, file = "MyData.csv")

# storing the confusion matrix into a table
Logistics_table1 <- data.frame(Confusion_model1)

# calculating the advertisement cost and loss for the this model and adding it as the columns to be implementedin R shiny
Logistics_table1 <- Logistics_table1 %>% mutate(ads = ifelse(pred == 'No', 0, Freq))
Logistics_table1 <- Logistics_table1 %>% 
                    mutate(Loss = ifelse(Churn == 'Yes', ifelse(pred == 'No',Freq*3,0),0))
Logistics_table1 <- Logistics_table1 %>% mutate(Total = Loss+ads)

#ROC
# pred <- predict(model1, teleco_train_1,type = 'prob') 
# predROC<- prediction(pred, teleco_train_1$Churn)
# roc <- performance(predroc, "tpr","fpr") #true positive rate
# plot(roc,colorize=T, main="ROC curve", ylab="Sensitivity" , xlab = "Accuracy" )
# #AUC
# #auc = performance(predroc, "auc")
# abline(a=0,b=1)
```

Logistic Regression model with threshold value 0.6

```{r}
teleco_test_1$pred<-'No'
teleco_test_1$pred[teleco_test_1$probability>0.6]<-'Yes'

# Confusion matrix
Confusion_model2 <- with(teleco_test_1,table(pred,Churn))
with(teleco_test_1,mean(pred==Churn))

# storing the confusion matrix into a table
Logistics_table2 <- data.frame(Confusion_model2)

# calculating the advertisement cost and loss for the this model and adding it as the columns to be implementedin R shiny
Logistics_table2 <- Logistics_table2 %>% mutate(ads = ifelse(pred == 'No', 0, Freq))
Logistics_table2 <- Logistics_table2 %>% 
                     mutate(Loss = ifelse(Churn == 'Yes', ifelse(pred == 'No',Freq*3,0),0))
Logistics_table2 <- Logistics_table2 %>% mutate(Total = Loss+ads)

```

Logistic Regression model with threshold value 0.7

```{r}
teleco_test_1$pred<-'No'
teleco_test_1$pred[teleco_test_1$probability>0.7]<-'Yes'

# Confusion matrix
Confusion_model3 <- with(teleco_test_1,table(pred,Churn))
with(teleco_test_1,mean(pred==Churn))

# storing the confusion matrix into a table
Logistics_table3 <- data.frame(Confusion_model3)

# calculating the advertisement cost and loss for the this model and adding it as the columns to be implementedin R shiny
Logistics_table3 <- Logistics_table3 %>% mutate(ads = ifelse(pred == 'No', 0, Freq))
Logistics_table3 <- Logistics_table3 %>% 
                     mutate(Loss = ifelse(Churn == 'Yes', ifelse(pred == 'No',Freq*3,0),0))
Logistics_table3 <- Logistics_table3 %>% mutate(Total = Loss+ads)

```

Logistic Regression model with threshold value 0.8

```{r}
teleco_test_1$pred<-'No'
teleco_test_1$pred[teleco_test_1$probability>0.8]<-'Yes'

# Confusion matrix
Confusion_model4 <- with(teleco_test_1,table(pred,Churn))
with(teleco_test_1,mean(pred==Churn))

# storing the confusion matrix into a table
Logistics_table4 <- data.frame(Confusion_model4)

# calculating the advertisement cost and loss for the this model and adding it as the columns to be implementedin R shiny
Logistics_table4 <- Logistics_table4 %>% mutate(ads = ifelse(pred == 'No', 0, Freq))
Logistics_table4 <- Logistics_table4 %>% 
                     mutate(Loss = ifelse(Churn == 'Yes', ifelse(pred == 'No',Freq*3,0),0))
Logistics_table4 <- Logistics_table4 %>% mutate(Total = Loss+ads)

```

Logistic Regression model with threshold value 0.4

```{r}
teleco_test_1$pred<-'No'
teleco_test_1$pred[teleco_test_1$probability>0.4]<-'Yes'

# Confusion matrix
Confusion_model5 <- with(teleco_test_1,table(pred,Churn))
with(teleco_test_1,mean(pred==Churn))

# storing the confusion matrix into a table
Logistics_table5 <- data.frame(Confusion_model5)
# to check the columns in the data frame
names(Logistics_table5)
# calculating the advertisement cost and loss for the this model and adding it as the columns to be implementedin R shiny
Logistics_table5 <- Logistics_table5 %>% mutate(ads = ifelse(pred == 'No', 0, Freq))
Logistics_table5 <- Logistics_table5 %>% 
                     mutate(Loss = ifelse(Churn == 'Yes', ifelse(pred == 'No',Freq*3,0),0))
Logistics_table5 <- Logistics_table5 %>% mutate(Total = Loss+ads)

```

 Model - 2 - Linear Discriminant Analysis Model (LDA)

```{r}
# Deleting the customerID column in both training and testing dataset
teleco_train_2 <- teleco_train
teleco_train_2['customerID'] <- NULL

teleco_test_2 <- teleco_test
teleco_test_2['customerID'] <- NULL

# fit the LDA model
model2 <- lda(Churn~.,data=teleco_train_2)
summary(model2)
model2$prior
# predictions
lda_predict = predict(model2,teleco_test_2)
lda_classify <- lda_predict$class
# a confusion matrix for the original and the predicted value is made
lda_output <- table(lda_classify,teleco_test_1$Churn)
# correct classification percentage
mean(lda_classify == teleco_test_2$Churn)
# musclassification error
mean(lda_classify != teleco_test_2$Churn )

# to create a table for the lds confusion matrix
lda_table <- data.frame(lda_output)
names(lda_table)

# calculating the advertisement cost and loss for the this model and adding it as the columns to be implementedin R shiny
lda_table <- lda_table %>% mutate(ads = ifelse(lda_classify == 'No', 0, Freq))
lda_table <- lda_table %>% 
             mutate(Loss = ifelse(Var2 == 'Yes', ifelse(lda_classify == 'No',Freq*3,0),0))
lda_table <- lda_table %>% mutate(Total = Loss+ads)
lda_table
```
 
Removing the dummy variables with the NA values in the training dataset

```{r}

teleco_train_3 <- teleco_train



teleco_train_3['Gender_Male'] <- NULL
teleco_train_3['SeniorCitizen_1'] <- NULL
teleco_train_3['Partner_No'] <- NULL
teleco_train_3['Dependents_Yes'] <- NULL
teleco_train_3['PhoneService_Yes'] <- NULL
teleco_train_3['MultipleLines_Nophoneservice'] <- NULL
teleco_train_3['MultipleLines_Yes'] <- NULL
teleco_train_3['InternetService_No'] <- NULL
teleco_train_3['OnlineSecurity_Yes'] <- NULL
teleco_train_3['OnlineSecurity_Nointernetservice'] <- NULL
teleco_train_3['Online_Backup_No'] <- NULL
teleco_train_3['Online_Backup_Nointernetservice'] <- NULL
teleco_train_3['DeviceProtection_Yes'] <- NULL                             
teleco_train_3['DeviceProtection_Nointernetservice'] <- NULL             
teleco_train_3['TechSupport_Yes'] <- NULL                                       
teleco_train_3['TechSupport_Nointernetservice'] <- NULL                    
teleco_train_3['tv_Yes'] <- NULL                                               
teleco_train_3['tv_Nointernetservice'] <- NULL                              
teleco_train_3['Movies_Yes'] <- NULL                                          
teleco_train_3['Movies_Nointernetservice'] <- NULL                       
teleco_train_3['Contract_Twoyear'] <- NULL                                   
teleco_train_3['PaperLessBilling_No'] <- NULL                                 
teleco_train_3['PaymentMethod_Creditcard_automatic'] <- NULL
teleco_train_nv3 <- teleco_train_3
teleco_train_3['customerID'] <- NULL

# Removing the dummy variables with the NA values in testing dataset

# ```{r}
teleco_test_3 <- teleco_test


teleco_test_3['Gender_Male'] <- NULL
teleco_test_3['SeniorCitizen_1'] <- NULL
teleco_test_3['Partner_No'] <- NULL
teleco_test_3['Dependents_Yes'] <- NULL
teleco_test_3['PhoneService_Yes'] <- NULL
teleco_test_3['MultipleLines_Nophoneservice'] <- NULL
teleco_test_3['MultipleLines_Yes'] <- NULL
teleco_test_3['InternetService_No'] <- NULL
teleco_test_3['OnlineSecurity_Yes'] <- NULL
teleco_test_3['OnlineSecurity_Nointernetservice'] <- NULL
teleco_test_3['Online_Backup_No'] <- NULL          
teleco_test_3['Movies_Yes'] <- NULL                                          
teleco_test_3['Movies_Nointernetservice'] <- NULL                       
teleco_test_3['Online_Backup_Nointernetservice'] <- NULL
teleco_test_3['DeviceProtection_Yes'] <- NULL                             
teleco_test_3['DeviceProtection_Nointernetservice'] <- NULL             
teleco_test_3['TechSupport_Yes'] <- NULL                                       
teleco_test_3['TechSupport_Nointernetservice'] <- NULL                    
teleco_test_3['tv_Yes'] <- NULL                                               
teleco_test_3['tv_Nointernetservice'] <- NULL                    
teleco_test_3['Contract_Twoyear'] <- NULL                                   
teleco_test_3['PaperLessBilling_No'] <- NULL                                 
teleco_test_3['PaymentMethod_Creditcard_automatic'] <- NULL
teleco_test_nv3 <- teleco_test_3
teleco_test_3['customerID'] <- NULL
```

 Model - 3 - Quadratic Discriminant Analysis model (QDA)

```{r}

# fit the QDA  model
model3 <- qda(Churn~.,data=teleco_train_3)
# predictions
qda_predict <- predict(model3,teleco_test_3)
qda_classify <- qda_predict$class
# a confusion matrix for the original and the predicted value is made
qda_output <- table(qda_classify,teleco_test_3$Churn)
# correct classification percentage
mean(qda_classify == teleco_test_3$Churn)
# musclassification error
mean(qda_classify != teleco_test_3$Churn)
qda_table <- data.frame(qda_output)
names(qda_table)

# calculating the advertisement cost and loss for the this model and adding it as the columns to be implementedin R shiny
qda_table <- qda_table %>% mutate(ads = ifelse(qda_classify == 'No', 0, Freq))
qda_table <- qda_table %>% 
             mutate(Loss = ifelse(Var2 == 'Yes', ifelse(qda_classify == 'No',Freq*3,0),0))
qda_table <- qda_table %>% mutate(Total = Loss+ads)
```

 Model - 4 - KNN model

```{r}

teleco_train_4 <- teleco_train
teleco_train_4['customerID'] <- NULL

teleco_test_4 <- teleco_test
teleco_test_4['customerID'] <- NULL

knntrain=teleco_train_4[,-4]
knntest=teleco_test_4[,-4]
knnlabel=teleco_train_4[,4]
dim(knntrain)
dim(knntest)

#knn.pred  No Yes
#    No   860 210
#    Yes  219 178
# mean :
# 0.707563

maxK = 1:25
accuracy = rep(x = 0, times = length(maxK))

for(i in seq_along(maxK)) {
  mgknn = knn(train = knntrain,
                test = knntest, 
                cl = knnlabel, 
                k = maxK[i])
  accuracy[i] = mean(teleco_test_4[,4]== mgknn)
}

{plot(accuracy, type = "b", col = "dodgerblue", cex = 1, pch = 10, 
     xlab = "k, number of neighbors", ylab = "classification accuracy",
     main = "Accuracy vs Neighbors")
# add lines indicating k with best accuracy
abline(v = which(accuracy == max(accuracy)), col = "darkorange", lwd = 1.5)
# add line for max accuracy seen
abline(h = max(accuracy), col = "grey", lty = 2)}


# for k =1
knn_pred =knn(knntrain,knntest,knnlabel,k=1)
knntable1 <- table(knn_pred,teleco_test_4$Churn)
knntable1 <- data.frame(knntable1)
knn_mean1 <- mean(knn_pred==teleco_test_4$Churn)
# calculating the advertisement cost and loss for the this model and adding it as the columns to be implementedin R shiny
knntable1 <- knntable1 %>% mutate(ads = ifelse(knn_pred == 'No', 0, Freq))
knntable1 <- knntable1 %>% 
             mutate(Loss = ifelse(Var2 == 'Yes', ifelse(knn_pred == 'No',Freq*3,0),0))
knntable1 <- knntable1 %>% mutate(Total = Loss+ads)

# for k =5
knn.pred2 =knn(knntrain,knntest,knnlabel,k=5)
knntable2 <- table(knn.pred2,teleco_test_4$Churn)
knntable2 <- data.frame(knntable2)
knn_mean2 <- mean(knn.pred2==teleco_test_4$Churn)
# calculating the advertisement cost and loss for the this model and adding it as the columns to be implementedin R shiny
knntable2 <- knntable2 %>% mutate(ads = ifelse(knn.pred2 == 'No', 0, Freq))
knntable2 <- knntable2 %>% 
             mutate(Loss = ifelse(Var2 == 'Yes', ifelse(knn.pred2 == 'No',Freq*3,0),0))
knntable2 <- knntable2 %>% mutate(Total = Loss+ads)

# for k =10
knn.pred3 =knn(knntrain,knntest,knnlabel,k=10)
knntable3 <- table(knn.pred3,teleco_test_4$Churn)
knntable3 <- data.frame(knntable3)
knn_mean3 <- mean(knn.pred3==teleco_test_4$Churn)
# calculating the advertisement cost and loss for the this model and adding it as the columns to be implementedin R shiny
knntable3 <- knntable3 %>% mutate(ads = ifelse(knn.pred3 == 'No', 0, Freq))
knntable3 <- knntable3 %>% 
             mutate(Loss = ifelse(Var2 == 'Yes', ifelse(knn.pred3 == 'No',Freq*3,0),0))
knntable3 <- knntable3 %>% mutate(Total = Loss+ads)

# for k =15
knn.pred4 =knn(knntrain,knntest,knnlabel,k=15)
knntable4 <- table(knn.pred4,teleco_test_4$Churn)
knntable4 <- data.frame(knntable4)
knn_mean4<- mean(knn.pred4==teleco_test_4$Churn)
# calculating the advertisement cost and loss for the this model and adding it as the columns to be implementedin R shiny
knntable4 <- knntable4 %>% mutate(ads = ifelse(knn.pred4 == 'No', 0, Freq))
knntable4 <- knntable4 %>% 
             mutate(Loss = ifelse(Var2 == 'Yes', ifelse(knn.pred4 == 'No',Freq*3,0),0))
knntable4 <- knntable4 %>% mutate(Total = Loss+ads)

# for k =21
knn.pred5 =knn(knntrain,knntest,knnlabel,k=21)
knntable5 <- table(knn.pred5,teleco_test_4$Churn)
knntable5 <- data.frame(knntable5)
knn_mean5 <- mean(knn.pred5==teleco_test_4$Churn)
# calculating the advertisement cost and loss for the this model and adding it as the columns to be implementedin R shiny
knntable5 <- knntable5 %>% mutate(ads = ifelse(knn.pred5 == 'No', 0, Freq))
knntable5 <- knntable5 %>% 
             mutate(Loss = ifelse(Var2 == 'Yes', ifelse(knn.pred5 == 'No',Freq*3,0),0))
knntable5 <- knntable5 %>% mutate(Total = Loss+ads)

```

Decision Tree

```{r}
teleco_train_5 <- teleco_train_3
teleco_train_5 <- data.frame(teleco_train_5)

teleco_test_5 <- teleco_test_3

#Fitting the tree
tree.teleco_train_5 = tree(Churn~., teleco_train_5)
summary(tree.teleco_train_5)
tree.teleco_train_5

#plot the tree
plot(tree.teleco_train_5)
text(a1, pretty = 0)
tree.teleco_train_5 # error correct

#Pruning the tree
set.seed(4)
cv.teleco_train_5 = cv.tree(tree.teleco_train_5, FUN = prune.misclass)
cv.teleco_train_5
#.................................
#plot the error rate as a function of both size and k; type "b" means both line and points
par(mfrow=c(1,2))
plot(cv.teleco_train_5$size, cv.teleco_train_5$dev, type = "b")
plot(cv.teleco_train_5$k, cv.teleco_train_5$dev, type = "b")

#Get the tree that gives the lowest error
prune.teleco_train_5 = prune.misclass(tree.teleco_train_5, best = 4)
plot(prune.teleco_train_5)
text(prune.teleco_train_5, pretty = 0) # error correct
prune.teleco_train_5

#For predictions of the tree, we use predict function. You may want to separate the dataset into train and test for this
tree.pred = predict(tree.teleco_train_5, teleco_test_5, type = "class")
dstree_confusion_matrix <- confusionMatrix(table(tree.pred,teleco_test_5$Churn))
dstree_table <- dstree_confusion_matrix$table 
decision_table <- data.frame(dstree_table)
#confusion matrix
#tree.pred   No  Yes
#      No  3880  882
#      Yes  254  560

#Now 79.62% of the test observations are correctly classi???ed, so not only has the pruning process
#produced a more interpretable tree, but it has also improved the classi???cation accuracy.

names(decision_table)
# calculating the advertisement cost and loss for the this model and adding it as the columns to be implementedin R shiny
decision_table <- decision_table %>% mutate(ads = ifelse(tree.pred == 'No', 0, Freq))
decision_table <- decision_table %>% 
                  mutate(Loss = ifelse(Var2 == 'Yes', ifelse(tree.pred == 'No',Freq*3,0),0))
decision_table <- decision_table %>% mutate(Total = Loss+ads)

```

Naive Bayes Model

```{r}
# Naive Bayes Theorem
# install.packages("e1071")
library(e1071)
library(caret) 
teleco_train_naive <- teleco_train_nv3
teleco_train_naive['customerID'] <- NULL
teleco_test_naive  <- teleco_test_nv3
teleco_test_naive['customerID'] <- NULL

class(teleco_train_naive)
# Fitting model
naive_model <- naiveBayes(Churn ~. , data = teleco_train_naive)
summary(naive_model)
#Predict Output 
naive_prediction= predict(naive_model,teleco_test_naive)
naive_confusion_matrix <- confusionMatrix(table(naive_prediction,teleco_test_naive$Churn))
naive_table <- naive_confusion_matrix$table 
naive_table1 <- data.frame(naive_table)
names(naive_table1)
teleco_test_nv3<- data.frame(teleco_test_nv3)
write.csv(teleco_test_nv3, file = "nb.csv")

naive_prediction<- data.frame(naive_prediction)
write.csv(naive_prediction, file = "nbpred.csv")


# calculating the advertisement cost and loss for the this model and adding it as the columns to be implementedin R shiny
naive_table1 <- naive_table1 %>% mutate(ads = ifelse(naive_prediction == 'No', 0, Freq))
naive_table1 <- naive_table1 %>% 
                mutate(Loss = ifelse(Var2 == 'Yes', ifelse(naive_prediction == 'No',Freq*3,0),0))
naive_table1 <- naive_table1 %>% mutate(Total = Loss+ads)
```

 Random Forest

```{r}


rfmodel <- randomForest(Churn~.,data = teleco_train_3,ntree=500)

plot(rfmodel)
summary(fit)
predicted= predict(rfmodel,teleco_test)
rf_confusion_matrix <- confusionMatrix(table(predicted,teleco_test_3$Churn))
rf_table<-rf_confusion_matrix$table
rf_table <- data.frame(rf_table)


rf_table <- rf_table %>% mutate(ads = ifelse(predicted == 'No', 0, Freq))
rf_table <- rf_table %>% 
                mutate(Loss = ifelse(Var2 == 'Yes', ifelse(predicted == 'No',Freq*3,0),0))
rf_table <- rf_table %>% mutate(Total = Loss+ads)

```

PCA

```{r}
library(pls)

teleco_train_6<-teleco_train_3
teleco_train_6$Churn = as.numeric(as.factor(teleco_train_6$Churn))
pcr.fit=pcr(Churn~ tenure + MonthlyCharges+TotalCharges, data=teleco_train_6, scale=TRUE, validation="CV")
summary(pcr.fit)

validationplot(pcr.fit, val.type="MSEP")

#To run the model again with the optimal number of components
pcr.fit=pcr(Churn~., data=teleco_train_6, scale=TRUE, ncomp = 1)
summary(pcr.fit)
```

Naive Bayes model with the churn prediction

```{r}
naive_final <- read.csv("naive_result.csv")

```
